Type-Safe Modular Parsing

### 2016-11-09 paper/sections/Library/ParsingLibrary.tex
Organize.

\subsection{Parsing Library}\label{subsec:parsinglibrary}

>>>>

\subsection{Fusion of Components/Concepts}

In the previous sections we have talked about open recursion and Object Algebras. These concepts will later be composed together for our
initial goal, which is to build extensible parsers, but surely it cannot live without a parsing library. But we want to argue here that besides
open recursion, which constructs the basis of extensibility in parsing, the other aspects are totally orthogonal, and hence can have their alternatives.
For example, Object Algebras are helpful to build extensible data structures, whereas an alternative with the same function can still be used. And a better
parsing library would introduce a lot of fancy features, nevertheless, it is independent from our key idea.

### 2016-11-09 paper/sections/ObjectAlgebras.tex
Organize.

\subsection{Object Algebras}\label{subsec:objectalgebras}

Object Algebras captures a design pattern to address the famous \textit{Expression Problem} nicely,
achieving two dimensions of extensibility (data variants and operations) in a modular and type-safe way.
Because of this, the definition of data structures is separated from behaviors on them, and future extensions
to both sides no longer require existing code to be modified, supporting separate compilation.

>>>>

\section{Object Algebras and Parsing}\label{sec:algebrasandparsing}

Object Algebras, first introduced by ... et al as a solution to the famous \textit{Expression Problem}, provide extensibility on
both data variants and operations for structures like abstract syntax trees. We integrate Object Algebras directly to enhance the
extensibility of open parsers.

\subsection{Object Algebras}\label{sec:objectalgebras}
Object Algebras captures a design pattern to address the Expression Problem nicely,
achieving two dimensions of extensibility (data variants and operations) in a modular and type-safe way.
Because of this, the definition of data structures is separated from behaviors on them, and future extensions
to both sides no longer require existing code to be modified, supporting separate compilation.
